### 2017-01-09 doc/manuscript.Rmd
Assigned the captions to figures and tables

```{r table_qic}
table_qic_main()
```

```{r table_basic}
table_basic()
```

```{r table_tagfa}
table_tagfa()
```

```{r table_gee}
table_gee_main(gee_unadj_df)
table_gee_main(gee_adj_df)
```

@@

```{r fig_tagfa}
plot_tagfa()
```

```{r fig_heatmap}
plot_heatmap(cor_df)
```
```{r fig_heatmap_tagfa}
plot_heatmap(cor_df_tagfa, text = FALSE)
```

```{r fig_gee_unadj}
plot_gee_main(gee_unadj_df)
```

```{r fig_gee_adj}
plot_gee_main(gee_adj_df)
```

```{r fig_pls}
gridExtra::grid.arrange(
    plot_pls(pls_homa2) + ggplot2::ggtitle('A: HOMA2-%S'), 
    plot_pls(pls_isi) + ggplot2::ggtitle('B: ISI'), 
    ncol = 2)
```

>>>>

```{r table_qic}
table_qic_main(caption = tab_qic)
```

```{r table_basic}
table_basic(caption = tab_basic)
```

```{r table_tagfa}
table_tagfa(caption = tab_tagfa)
```

```{r table_gee}
table_gee_main(gee_unadj_df, caption = tab_gee_unadj)
table_gee_main(gee_adj_df, caption = tab_gee_adj)
```

@@

```{r fig_tagfa, fig.cap=fig_tagfa}
plot_tagfa()
```

```{r fig_heatmap, fig.cap=fig_heatmap}
plot_heatmap(cor_df)
```

```{r fig_heatmap_tagfa, fig.cap=fig_heatmap_tagfa}
plot_heatmap(cor_df_tagfa, text = FALSE)
```

```{r fig_gee_unadj, fig.cap=fig_gee_unadj}
plot_gee_main(gee_unadj_df)
```

```{r fig_gee_adj, fig.cap=fig_gee_adj}
plot_gee_main(gee_adj_df)
```

```{r fig_pls, fig.cap=fig_pls}
gridExtra::grid.arrange(
    plot_pls(pls_homa2) + ggplot2::ggtitle('A: HOMA2-%S'), 
    plot_pls(pls_isi) + ggplot2::ggtitle('B: ISI'), 
    ncol = 2)
```
